Visualisation of Brain Statistics with R-package `ggseg`

### 2019-04-15 draft_1_AMM.rmd
Update draft_1_AMM.rmd

# Author Contributions
DVP designed the earliest 2D polygon plotting functionality together with the initial scripts, and contributed to the image-to-polygon and the image-to-mesh pipelines. 
Athanasia M. Mowinckel adapted the initial scripts and made the functions into package format and making the functions more user-friendly.
She also was responsible for adding the mesh-plot functionality through plotly, and developing the pipeline for making that possible. 
A. M. Mowinckel wrote the first draft of the paper, and both have since critically edited it.

@@

# Acknowledgements
We particularly thank Anders M Fjell and Kristine B Walhovd for insightful discussion and funding support and Ingle K Amlien for inspiration and code comments. 
We also thank John Muschelli for his initial improvements in the package code and preparing it for incorporation in neuroconductor (-@neuroconductor), and Richard Beare for submitting the first community created atlas, and providing helpful comments to the base code.

# Funding 
This work is funded by EU Horizon 2020 Grant 'Healthy minds 0-100 years: Optimising the use of European brain imaging cohorts (Lifebrain)', with grant agreement number 732592 and ERC Starting Grant schemes (grant agreements 283634, 725025 and 313440).

>>>>

# Author Contributions
DVP designed the earliest 2D polygon plotting functionality together with the initial scripts and contributed to the image-to-polygon and the image-to-mesh pipelines. 
Athanasia M. Mowinckel adapted the initial scripts and made the functions into package format and making the functions more user-friendly.
She also was responsible for adding the mesh-plot functionality through plotly, and developing the pipeline for making that possible. 
A. M. Mowinckel wrote the first draft of the paper, and both have since critically edited it.

@@

# Acknowledgements
We particularly thank Anders M Fjell and Kristine B Walhovd for insightful discussion and funding support and Ingle K Amlien for inspiration and code comments. 
We also thank John Muschelli for his initial improvements in the package code and preparing it for incorporation in neuroconductor (-@neuroconductor) and Richard Beare for submitting the first community created atlas, and providing helpful comments to the base code.

# Funding 
This work is funded by EU Horizon 2020 Grant 'Healthy minds 0-100 years: Optimising the use of European brain imaging cohorts (Lifebrain)', with grant agreement number 732592 and ERC Starting Grant schemes (grant agreements 283634, 725025, and 313440).
